Fractional land cover classification method assessment using PROBA-V satellite data

### 2019-04-16 article/article.tex
Addition of accuracy statistics table

% Minimalistic template for a generic article, geared towards MDPI guidelines
% Use PDFLaTeX
\documentclass[a4paper,10pt]{article}
% Packages provided by the MDPI template already
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{indentfirst}

@@

% Acronyms - cite with \ac{}
\newacronym{GNSS}{GNSS}{Global Navigation Satellite System}
\makenoidxglossaries

@@

\begin{enumerate}
 \item RMSE, MAE, ME per class
 \item Sub-pixel confusion-uncertainty matrix: kappa, OA, PA, UA
 \item Correlation matrix
 \item Prediction accuracy at different parts of the predicted vs observed line
 \item Comparison with a control/intercept model (10\% of everything)?
\end{enumerate}

@@

>>>>

% Minimalistic template for a generic article, geared towards MDPI guidelines
% Use PDFLaTeX
\documentclass[a4paper,10pt]{article}
% Packages provided by the MDPI template already
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{indentfirst}
\usepackage{booktabs} % For \toprule, etc.

@@

% Acronyms - cite with \ac{}
\newacronym{GNSS}{GNSS}{Global Navigation Satellite System}
\newacronym{OA}{OA}{Overall accuracy}
\newacronym{UA}{UA}{User accuracy}
\newacronym{PA}{PA}{Producer accuracy}
\newacronym{RMSE}{RMSE}{Root mean squared error}
\newacronym{MAE}{MAE}{Mean absolute error}
\newacronym{ME}{ME}{Mean error}
\newacronym{NSE}{NSE}{Nash–Sutcliffe model efficiency coefficient}
\makenoidxglossaries

@@

\begin{enumerate}
 \item \ac{RMSE}, \ac{MAE}, \ac{ME} per class
 \item Sub-pixel confusion-uncertainty matrix: kappa, \ac{OA}, \ac{PA}, \ac{UA}
 \item Correlation matrix
 \item Prediction accuracy at different parts of the predicted vs observed line
 \item Comparison with a control/intercept model (10\% of everything)?
\end{enumerate}

@@

\subsection{Method accuracy comparison}

The intercept model (always predicting the mean) achieves an \ac{RMSE} of 30\%, and \ac{OA}

Logistic regression achieved RMSE of 18.7\%, MAE of 9.8\%,

\begin{table}
\centering
\begin{tabular}{llllll}
\toprule
\textbf{Model} & \textbf{\ac{RMSE} (\%)} & \textbf{\ac{MAE} (\%)} & \textbf{\acrshort{NSE}} & \textbf{\ac{OA} (\%)} & \textbf{Kappa} \\
\midrule
Intercept
& 30    &       &       & 25±4  & 0.1       \\
Fuzzy nearest centroid
& 22    &       &       & 49    & 0.41      \\
Neural networks
& 19.5  &       &       &       &           \\
PLS regression
& 19    &       &       & 47±5  & 0.36±0.07 \\
Logistic regression
& 18.7  & 9.8   &       & 66±4  & 0.57      \\
Lasso regression
& 18.5  &       &       &       &           \\
Random forest
& 16.6  & 9.2   & 0.67  & 68±4  & 0.60      \\
\ensuremath{''} histogram matched
& 22.0  & 9.7   & 0.43  & 66±2  & 0.58±0.03 \\
\ensuremath{''} two-step
& 18.3  & 8.0   & 0.59  & 72±2  & 0.63      \\
\ensuremath{''} three-step
& 18.6  & 8.2   & 0.59  & 71±4  & 0.64      \\
\ensuremath{''} \ensuremath{''} histogram matched
& 21.3  & 9.1   & 0.46  & 68±3  & 0.61      \\
\bottomrule
\end{tabular}
\caption{Accuracy statistics of the models tested.}
\label{tab-accuracy}
\end{table}
